\begin{thebibliography}{99}
\setlength{\itemsep}{0.3in}
\bibitem{bib1}
Van de Hulst, H.C., 1957. \textit{Light Scattering by Small Particles}, Wiley, New York.
\bibitem{bib2}
Bohren, C. F., and D. R. Huffman, 1998. \textit{Absorption and Scattering of Light by Small Particles}, Wiley, New York.
\bibitem{bib3}
Ishimaru, A., 1978. \textit{Wave Propagation and Scattering in Random Media}, Academic, San Diego.
\bibitem{bib4}
Tsang, L., J. Kong, and K-H. Ding, 2000. \textit{Scattering of Electromagnetic Waves: Theories and Applications}, Wiley, New York.
\bibitem{bib5}
Stratton, A. J., 1941. \textit{Electromagnetic Theory},McGraw-Hill, New York.
\bibitem{bib6}
Kerker, M., 1969. \textit{The scattering of light and other electromagnetic radiation}, Academic, San Diego.
\bibitem{bib7}
Born. M., and E. Wolf, 1965. \textit{Principles of Optics: Electromagnetic Theory of Propagation, Interference and Diffraction of Light}, Pergamon, Oxford.
\bibitem{bib8}
Mie, G., 1908. Beitr{\"a}ge zur Optik tr{\"u}ber Medien, speziell kolloidaler Metall{\"o}sungen, \textit{Ann Phys.}, \textbf{330}, 377\textendash 445.
\bibitem{bib9}
 Brillouin, L., 1949. The Scattering Cross Section of Spheres for Electromagnetic Waves, \textit{J. Appl. Phys.} \textbf{20}, 1110\textendash 1125.
\bibitem{bib10}
Stokes, G. G., 1852. On the composition and resolution of streams of polarized light from different sources, \textit{Trans. Camb. Philos. Soc.}, \textbf{9}, 399\textendash 416.
\bibitem{bib11}
Wait, J. R., 1965. Scattering of a plane wave from a circular dielectric cylinder at oblique incidence,  \textit{Can. J. Phys.}, \textbf{33}, 189\textendash 195.
\bibitem{bib12}
Wait, J. R., 1959. \textit{Electromagnetic radiation from cylindrical structures}, Pergamon, New York.
\bibitem{bib13}
Farone, W. A., and C. W. Querfeld, 1965. \textit{report ERDA-287}, U. S. Army Electronics Research and Development Activity, WhiteSands Missile Range, New Mexico.
\bibitem{bib14}
Kerker, M., D. Cooke, A. W. Farone, R. A. Jacobsen, 1966. Electromagnetic scattering from an infinite circular cylinder at oblique incidence: I. radiance functions for \(m = 1.46\),
\textit{J. Opt. Soc. Am.}, \textbf{56}, 487\textendash 489.
\bibitem{bib15}
Sihvola, A., 1999. \textit{Electromagnetic mixing formulas and applications}, The IET, London.
\bibitem{bib16}
Cai, W., U. K. Chettiar, A. V. Kildishev, R. A. Jacobsen, and V. M. Shalaev, 2007. Optical cloaking with metamaterials,
\textit{Nat. Photonics}, \textbf{1}, 224\textendash 227.
\bibitem{bib17}
Mundru, P. C., V. K. Pappakrishnan, and D. A Genov, 2012. Material- and geometry-independent multishell cloaking device, \textit{Phys. Rev. B}, \textbf{85}, 045402.
\bibitem{bib18}
Al{\'u}, A., and N. Engheta, 2005. Achieving transparency with plasmonic and metamaterial coatings, \textit{Phys. Rev. E}, \textbf{72}, 016623.
\bibitem{bib19}
Zhou, X., and G. Hu, 2006. Design for electromagnetic wave transparency with metamaterials, \textit{Phys. Rev. E}, \textbf{74}, 026607.
\bibitem{bib20}
Leonhardt, U., and T. Philbin, 1999. \textit{Geometry and Light: The Science of Invisibility}, Dover, New York.
\bibitem{bib21}
Xu, H., 2005. Multilayered metal core-shell nanostructures for inducing a large and tunable local optical field, \textit{Phys. Rev. B}, \textbf{72}, 073405.
\bibitem{bib22}
Jacob, Z., L. V. Alekseyev, and E. Narimanov, 2006. Optical hyperlens: Far-field imaging beyond the diffraction limit, \textit{Opt. Express}, \textbf{14}, 8247\textendash 8256.
\bibitem{bib23}
Liu, Z., H. Lee, Y. Xiong, C. Sun, and X. Zhang, 2007. Far-field optical hyperlens magnifying sub-diffraction-limited objects, \textit{Science}, \textbf{315}, 1686.
\bibitem{bib24}
Lu{\'k}Yanchuk, B., N. I. Zheludev, S. A. Maier, N. J. Halas, P. Nordlander, H. Giessen, and C. T. Chong, 2010. The Fano resonance in plasmonic nanostructures and metamaterials, \textit{Nat. Materials}, \textbf{9}, 707\textendash 715.
\bibitem{bib25}
Bergman, D.J., and D. Stroud, 1992. Physical Properties of Macroscopically Inhomogeneous Media, \textit{Solid State Phys.}, \textbf{46}, 147\textendash 269.
\bibitem{bib26}
Jackson, J. D., 1999. \textit{Classical electrodynamics}, John Wiley, Hoboken.
\bibitem{bib27}
Bergman, D.J., and D. Stroud, 1992. Physical Properties of Macroscopically Inhomogeneous Media, \textit{Solid State Phys.}, \textbf{46}, 419\textendash 440.
\bibitem{bib28}
Genov, D. A., A. K. Sarychev, and V. M. Shalaev,  2003. Metal-dielectric composite filters with controlled spectral windows of transparency, \textit{J. Nonlinear Opt. Phys. Mater.}, \textbf{12}, 385\textendash 420.
\bibitem{bib29}
Bruggeman, D. A. G.,  1935. Berechnung verschiedener physikalischer Konstanten von heterogenen Substanzen. I. Dielektrizit\"{a}tskonstanten und Leitf\"{a}higkeiten der Mischk\"{o}rper aus isotropen Substanzen, \textit{Ann. Phys. (\textit{Leipzig})}, \textbf{24}, 636\textendash 664.
\bibitem{bib30}
Polder, D., and J. H.  Van Santeen, 1946. The effective permeability of mixtures of solids, \textit{Physica}, \textbf{12}, 257\textendash 271.
\bibitem{bib31}
Golovan. L. A.,  V. Yu. Timoshenko, and P. K. Kashkarov, 2007. Optical properties of porous-system-based nanocomposites, \textit{Phys.-Usp.}, \textbf{50}, 595\textendash 612.
\bibitem{bib32}
Doyle, W.T., 1989. Optical properties of a suspension of metal spheres, \textit{Phys. Rev. B}, \textbf{39}, 9852\textendash 9858.
\bibitem{bib33}
Lakhtakia, A., 1992. Size\textendash dependent Maxwell–Garnett formula from an integral equation formalism, \textit{Optik}, \textbf{91}, 134\textendash 137.
\bibitem{bib34}
Foss, C. A., G. L. Hornyak, J. A. Stockert, and C. R. Martin, 1994. Template-Synthesized nanoscopic gold particles: optical spectra and the effects of particle size and shape, \textit{J. Phys. Chem.}, \textbf{98}, 2963\textendash 2971.
\bibitem{bib35}
Dungey, C. E., and C. F. Bohren,  1991. Light scattering by nonspherical particles: a refinement to the coupled-dipole method, \textit{J. Opt. Soc. Am. A}, \textbf{8}, 81\textendash 87.
\bibitem{bib36}
Stroud, D., 1975. Generalized effective-medium approach to the conductivity of an inhomogeneous material, \textit{Phys. Rev. B}, \textbf{12}, 3368\textendash 3373.
\bibitem{bib37}
Abeles, B., and J. I. Gittleman, 1976. Composite material films: optical properties and applications, \textit{Appl. Opt.}, \textbf{15}, 2328\textendash 2332.
\bibitem{bib38}
Landauer, R., 1952. The Electrical Resistance of Binary Metallic Mixtures, \textit{J. Appl. Phys.}, \textbf{23}, 779\textendash 784.
\bibitem{bib39}
Cummer, S. A., B. I. Popa, D. Schurig, D. R. Smith, and J. Pendry, 2006. Full-wave simulations of electromagnetic cloaking structures,
\textit{Phys. Rev. E}, \textbf{74}, 036621.
\bibitem{bib40}
Leonhardt, U., 2006. Optical conformal mapping,
\textit{Science}, \textbf{312}, 1777\textendash 1780.
\bibitem{bib41}
Pendry, J. B., D. Schurig, and D. R. Smith, 2006. Controlling electromagnetic fields, \textit{Science}, \textbf{312}, 1780\textendash 1782.
\bibitem{bib42}
Leonhardt, U., and T. Philbin, 2006. General relativity in electrical engineering, \textit{New J. Phys.}, \textbf{8}, 247.
\bibitem{bib43}
Wait, J.R., 1985. \textit{Electromagnetic wave theory}, Harper \& Row, New York.
\bibitem{bib44}
Harrington, R.F., 1961. \textit{Time harmonic electromagnetic fields}, McGraw-HILL, New York.
\bibitem{bib45}
Genov, D.A.,  R.F. Oulton, G. Bartal, and X. Zhang, 2011.
Anomalous spectral scaling of light emission rates in low-dimensional metallic nanostructures, \textit{Phys. Rev. B}, \textbf{83}, 245312.
\bibitem{bib46}
Prodan, E.,  C.  Radloff, N.J. Halas,  and P. Nordlander,  2003.
A Hybridization Model for the Plasmon Response of Complex Nanostructures, \textit{Science}, \textbf{302}, 419\textendash 422.
\bibitem{bib47}
Huang. Y., Y. Feng, and T. Jiang, 2007. Electromagnetic cloaking by layered structure of homogeneous isotropic materials,  \textit{Opt. Express}, \textbf{15}, 11133\textendash 11141.
\bibitem{bib48}
Palik. E., 1997. \textit{Handbook of Optical Constants of Solids}, Academic Press, London.
\bibitem{bib49},
Lai. Y., N. Jack, H. Chen, D. Han, J. Xiao, Z-Q. Zhang, and  C. T. Chan, 2009. Illusion Optics: The Optical Transformation of an Object into Another Object,  \textit{Phys. Rev. Lett.}, \textbf{102}, 253902.
\bibitem{bib50}
Pendry. J. B., and S.A. Ramakrishna, 2002. Near-field lenses in two dimensions, \textit{J. Phys.: Condens. Matter}, \textbf{14}, 8463\textendash 8479.
\bibitem{bib51}
McCall M. W.,  A. Favaro, P. Kinsler and A. Boardman, 2011. 
A spacetime cloak, or a history editor, \textit{J. Opt.}, \textbf{13}, 024003.
\bibitem{bib52} 
Kerker. M., 1975. Invisible bodies, \textit{J. Opt. Soc. Am.}, \textbf{65}, 376\textendash 379.
\bibitem{bib53}
Kerker, M., 1982. Lorenz-Mie Scattering by Spheres: Some Newly Recognized Phenomena, \textit{Aerosol. Sci. Technol.}, \textbf{1}, 275\textendash 291.
\bibitem{bib54}
Dentcho. D. A., P. C. Mundru, 2014. Quasi-effective medium theory for multilayered magneto-dielectric structures, \textit{J. Opt.}, \textbf{16}, 015101.
\bibitem{bib55}
Bohm, D., 1951. \textit{Quantum theory}, Prentice\textendash Hall, New York.
\bibitem{bib56}
Schiff. L. I., 1955. \textit{Quantum mechanics}, McGraw\textendash Hill, New York.
\bibitem{bib57}
Rayleigh. J. W. S., 1878. \textit{The Theory of Sound vol.II}, Macmillan, London.
\bibitem{bib58}
Fax\'{e}n. H., J. Holtsmark, 1927. Beitrag zur Theorie des Durchganges langsamer Elektronen durch Gase, \textit{Zeits. f. Physik}, \textbf{45}, 307\textendash 324.

\end{thebibliography}
